Supplementary figures for Detailed disease progression of 213 patients hospitalized with Covid-19 in the Czech Republic: An exploratory analysis

### 2020-12-22 manuscript/manuscript.Rmd
Applied minor tweks from feedback

Favipiravir is one of the less explored experimental treatments, previously used for influenza including avian types, with only one larger RCT in Covid- 19 known to us [@http://zotero.org/users/5567156/items/ISLSL7UC], the study however has many potentially severe problems [@http://zotero.org/users/5567156/items/7HDXLWEA]. Other studies are scarce - even when considering very small studies and case series [@http://zotero.org/users/5567156/items/F3VNTQ92; @http://zotero.org/users/5567156/items/FSUQMUP8; @http://zotero.org/users/5567156/items/894H9N9B]. None of the results allow strong conclusions about benefits or harms of favipiravir, although a  metaanalysis of all available small studies showed an effect of favipiravir on clinical improvement in mild and moderate disease [@http://zotero.org/users/5567156/items/7595KBWR].
For additional summary of treatments under investigation see Siemieniuk et al. [@http://zotero.org/users/5567156/items/YP62P6XJ]

>>>>

Favipiravir is one of the less explored experimental treatments, previously used for influenza including avian types, with only one larger RCT in Covid- 19 known to us [@http://zotero.org/users/5567156/items/ISLSL7UC], the study however has many potentially severe problems [@http://zotero.org/users/5567156/items/7HDXLWEA]. Other studies are scarce - even when considering very small studies and case series [@http://zotero.org/users/5567156/items/F3VNTQ92; @http://zotero.org/users/5567156/items/FSUQMUP8; @http://zotero.org/users/5567156/items/894H9N9B]. None of the results allow strong conclusions about benefits or harms of favipiravir, although a  metaanalysis of all available small studies showed an effect of favipiravir on clinical improvement in mild and moderate disease [@http://zotero.org/users/5567156/items/7595KBWR].
For additional summary of treatments under investigation see Siemieniuk et al. [@http://zotero.org/users/5567156/items/YP62P6XJ]. There is also an emerging consensus on the importance of prophylactic anticoagulation therapy in managing hospitalized patients with Covid-19, although clinical trials to validate this approach are still ongoing[@http://zotero.org/users/5567156/items/5ZW5JM8R].

### 2020-12-22 manuscript/supplementary_figures.Rmd
Applied minor tweks from feedback

---
title: "Supplementary figures for Detailed disease progression of 213 patients hospitalized with Covid-19 in the Czech Republic: An exploratory analysis" 
output: 
  #rticles::arxiv_article
  # bookdown::pdf_document2:
  #    toc: false
  bookdown::word_document2: 
    toc: false
    reference_docx: "output_template.docx"
date: "Version: `r format(Sys.time(), '%Y-%m-%d')`"
---

@@

```{r markeroverlaps, fig.cap = "Density plots of worst marker values per patient, stratified by worst condition experienced by the patient.", fig.height=6}
frac <- 0.2
data$marker_data %>% filter(marker %in% c("lymphocyte_count", "d_dimer", "CRP", "IL_6")) %>%
  inner_join(data$patient_data, by = c("hospital_id", "patient_id")) %>%
  #filter(worst_breathing %in% c("AA", "Death")) %>%
  group_by(marker, patient_id, worst_breathing_s) %>%
  summarise(worst_value = case_when(marker == "lymphocyte_count" ~ min(log10(value)),
                                    marker == "IL_6" ~ max(log10(value)),
                                    TRUE ~ max(value)),
            .groups = "drop") %>% 
  filter(!is.infinite(worst_value)) %>%
  mutate(marker = factor(marker, levels = c("lymphocyte_count", "d_dimer", "CRP", "IL_6"),
         labels = c("Lowest Log10(lymphocyte count)", "Highest D-dimer", "Highest CRP", "Highest Log10(IL_6)"))) %>%
  ggplot(aes(x = worst_value, color = worst_breathing_s, fill = worst_breathing_s, group = worst_breathing_s)) +
  geom_density(adjust = 2, alpha = 0.3) +
  scale_color_viridis_d("Worst condition") +
  scale_fill_viridis_d("Worst condition") +
  scale_x_continuous("Marker value") +
  facet_wrap(~marker, scales = "free", ncol = 1)

>>>>

---
title: "Supplementary figures for Detailed disease progression of 213 patients hospitalized with Covid-19 in the Czech Republic: An exploratory analysis" 
output: 
  #rticles::arxiv_article
  # bookdown::pdf_document2:
  #    toc: false
  bookdown::word_document2: 
    toc: false
    reference_docx: "output_template.docx"
#date: "Version: `r format(Sys.time(), '%Y-%m-%d')`"
---

@@

```{r markeroverlaps, fig.cap = "Density plots of worst marker values per patient, stratified by worst condition experienced by the patient. For each patient that had a given marker measured, the worst value was taken. Additionally the patients are classified by the worst condition (regardless of the timing relative to the worst marker levels). For each set of patients and marker an empirical density plot of the worst marker values is shown.", fig.height=6}
frac <- 0.2
data$marker_data %>% filter(marker %in% c("lymphocyte_count", "d_dimer", "CRP", "IL_6")) %>%
  inner_join(data$patient_data, by = c("hospital_id", "patient_id")) %>%
  #filter(worst_breathing %in% c("AA", "Death")) %>%
  group_by(marker, patient_id, worst_breathing_s) %>%
  summarise(worst_value = case_when(marker == "lymphocyte_count" ~ min(log10(value)),
                                    marker == "IL_6" ~ max(log10(value)),
                                    TRUE ~ max(value)),
            .groups = "drop") %>% 
  filter(!is.infinite(worst_value)) %>%
  mutate(marker = factor(marker, levels = c("lymphocyte_count", "d_dimer", "CRP", "IL_6"),
         labels = c("Lowest Log10(lymphocyte count)", "Highest D-dimer", "Highest CRP", "Highest Log10(IL_6)"))) %>%
  ggplot(aes(x = worst_value, color = worst_breathing_s, fill = worst_breathing_s, group = worst_breathing_s)) +
  geom_density(adjust = 2, alpha = 0.3) +
  scale_color_viridis_d("Worst condition") +
  scale_fill_viridis_d("Worst condition") +
  scale_x_continuous("Marker value") +
  facet_wrap(~marker, scales = "free", ncol = 1)
